Species with high control capacity support stable coexistence of pollination networks

### 2018-07-17 paper/reviewers-response.Rmd

---
title: "Structural controllability of ecological networks"
subtitle: "JEcol-2017-0720 - Detailed response to comments"
author: "Fernando Cagua, Kate L. Wootton, Daniel B. Stouffer"
classoption: a4paper
csl: journal-of-ecology.csl
documentclass: artikel1
output: 
  bookdown::pdf_document2: 
    keep_tex: yes
    toc: false
    number_sections: false
header-includes:
  - \usepackage{setspace}
  - \usepackage{xr}
  - \usepackage{lineno}
  - \newcommand{\R}[1]{\label{#1}\linelabel{#1}}
  - \newcommand{\lr}[1]{page~\pageref{#1}, line~\lineref{#1}}
  - \externaldocument[M-]{manuscript}
  - \externaldocument[S-]{supp-info}
  - \usepackage[most]{tcolorbox}
  - \definecolor{block-gray}{gray}{0.9}
  - \newtcolorbox{myquote}{colback=block-gray,grow to right by=-10mm,grow to left by=-10mm, boxrule=0pt,boxsep=0pt,breakable}
---

\doublespacing

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, 
                      warning = FALSE)
```

We are thankful to the assistant editor James Ross, the editors Nicole Rafferty and David Gibson, and two anonymous reviewers for the insightful comments to improve the manuscript. 
In the following sections, you can find a detailed response to each comment raised during the previous round of review.

### 2018-07-17 paper/manuscript.Rmd
Narrow down titles

---
title: "Structural controllability of ecological networks"
classoption: a4paper
csl: journal-of-ecology.csl
output: 
  bookdown::pdf_document2: 
    keep_tex: yes
    number_sections: false
toc: false
header-includes:
- \usepackage{geometry}
# - \geometry{right=3in,marginparwidth=2.5in}
- \usepackage{setspace}
- \usepackage{float}
- \usepackage{booktabs}
- \usepackage{caption}
- \usepackage{lineno}
- \newcommand{\R}[1]{\label{#1}\linelabel{#1}}
- \newcommand{\lr}[1]{page~\pageref{#1}, line~\lineref{#1}}
- \usepackage{xr}
- \externaldocument[S-]{supp-info}
- \usepackage{siunitx}
- \usepackage{multirow}
- \usepackage{makecell}
- \usepackage{threeparttablex}
documentclass: artikel1
bibliography: phd-bibliography/network-control.bib
---

@@

* Keystoneness, centrality, and the structural controllability of ecological networks

>>>>

---
title: "Species with high control capacity support stable coexistence of pollination networks"
classoption: a4paper
csl: journal-of-ecology.csl
output: 
  bookdown::pdf_document2: 
    keep_tex: yes
    number_sections: false
toc: false
header-includes:
- \usepackage{geometry}
# - \geometry{right=3in,marginparwidth=2.5in}
- \usepackage{setspace}
- \usepackage{float}
- \usepackage{booktabs}
- \usepackage{caption}
- \usepackage{lineno}
- \newcommand{\R}[1]{\label{#1}\linelabel{#1}}
- \newcommand{\lr}[1]{page~\pageref{#1}, line~\lineref{#1}}
- \usepackage{xr}
- \externaldocument[S-]{supp-info}
- \usepackage{siunitx}
- \usepackage{multirow}
- \usepackage{makecell}
- \usepackage{threeparttablex}
documentclass: artikel1
bibliography: phd-bibliography/network-control.bib
---

@@

* Structural controllability of ecological networks
* Structural controllability: species with high control capacity support stable coexistence of pollination networks
